Secure Composition of Robust and Optimising Compilers

### 2024-09-08 tech/main.tex

\begin{definition}{\definitionlabel[Function Composition]{function-composition}}
  $\fncompo{f}{g}\isdef \lambda x.f(g\;x)$
\end{definition}

@@

>>>>

\begin{definition}{\definitionlabel[Function Composition]{function-composition}}
  $\fncompo{f}{g}\isdef \lambda x.g(f\;x)$
\end{definition}

@@

\begin{lemma}{\lemmalabel[Trace Relation distributes on Universal Image]{xtrace-distribute-universal}}
  Let $X$ be either a trace-property or a class. Then:
  \begin{goals}
    \goal{xtrace-distribute-universal}{\mapUniversal{\fncompo{\sim_1}{\sim_2}}{X} = \mapUniversal{\sim_2}{\mapUniversal{\sim_1}{X}}}
  \end{goals}
\end{lemma}
\begin{proof}
  Straightforward unfolding of \definitionref{universal-image} and \definitionref{function-composition} in \goalref{xtrace-distribute-universal}.
\end{proof}
\begin{lemma}{\lemmalabel[Trace Relation distributes on Existential Image]{xtrace-distribute-existential}}
  Let $X$ be either a trace-property or a class. Then:
  \begin{goals}
    \goal{xtrace-distribute-existential}{\mapExistential{\fncompo{\sim_1}{\sim_2}}{X} = \mapExistential{\sim_2}{\mapExistential{\sim_1}{X}}}
  \end{goals}
\end{lemma}
\begin{proof}
  Straightforward unfolding of \definitionref{existential-image} and \definitionref{function-composition} in \goalref{xtrace-distribute-existential}.
\end{proof}
